Structured Versus Decorated Cospans

### 2021-01-04 cospans.tex
small changes

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/12/31

@@

Similarly the right and left unitors can be constructed: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with the isomorphism between decorations
\begin{displaymath}
 \scalebox{.9}
{\begin{tikzcd}[row sep=.15in,ampersand replacement=\&]
1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{m,a}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a\times1)"'] \&\&  \\
1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m)
 \end{tikzcd}}
\end{displaymath}
All data can be verified to satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
\end{proof}

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/2

@@

The right and left unitors are defined similarly: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with this isomorphism between decorations:
\begin{displaymath}
 \scalebox{.9}
{\begin{tikzcd}[row sep=.15in,ampersand replacement=\&]
1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{m,a}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a\times1)"'] \&\&  \\
1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m).
 \end{tikzcd}}
\end{displaymath}
All data can be verified to satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
\end{proof}
